How cryptic is cryptic diversity? Machine learning approaches to classifying morphological variation in \textit{Emys marmorata} (Testudinoidea, Emydidae).

### 2013-08-12 documents/turtle_paper.Rnw
made tps grids prettier. ellipses.

\begin{figure}[ht]
  \centering
  \includegraphics{figure/gap_map}
  \caption{Clustering solution for PAM with two mediods for the entire set of observed \textit{E. marmorata}. Clustering was based entirely on the \(\rho\) dissimilarity matrix of ``half'' plastral landmark configurations following Procrustes superimposition.}
  \label{fig:gap_map}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width = \textwidth]{figure/gen_map}
  \caption{Comparison between reference classification of testing data set (upper left) and the estimated classifications based on the selected LDA-based classification (lda, upper right), multinomial logistic regression (multi, lower left) and random forest models (rf, lower right). Classification corresponds to the four classes as suggested by the hypothesis of \citet{Spinks2005} and \citet{Spinks2010}.}
  \label{fig:gen_map}
\end{figure}

% mean shapes of all the classes
\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.4\textwidth}
    \centering
    \includegraphics[width = \textwidth]{figure/mshape_1}
    \caption{Northern}
    \label{fig:mean_shape1}
  \end{subfigure}
  \begin{subfigure}[b]{0.4\textwidth}
    \centering
    \includegraphics[width = \textwidth]{figure/mshape_2}
    \caption{Eastern}
    \label{fig:mean_shape2}
  \end{subfigure}
  % new line. might want to make these closer together

  \begin{subfigure}[b]{0.4\textwidth}
    \centering
    \includegraphics[width = \textwidth]{figure/mshape_3}
    \caption{Western}
    \label{fig:mean_shape3}
  \end{subfigure}
  \begin{subfigure}[b]{0.4\textwidth}
    \centering
    \includegraphics[width = \textwidth]{figure/mshape_4}
    \caption{Southern}
    \label{fig:mean_shape4}
  \end{subfigure}
  \caption{Thin-plate splines for each of the four classes from the best classification hypothesis based on the generalization results (Fig. \ref{fig:gen_res}). The four different classes are labeled according to the biogeographic groups as depicted in figure \ref{fig:gen_map}. The deformations are depicted with 2x magnification from base.}
  \label{fig:mean_shape}
\end{figure}

>>>>

\begin{figure}[ht]
  \centering
  \includegraphics{figure/gap_map}
  \caption{Clustering solution for PAM with two mediods for the entire set of observed \textit{E. marmorata}. Clustering was based entirely on the \(\rho\) dissimilarity matrix of ``half'' plastral landmark configurations following Procrustes superimposition. Point shapes correspond to the two clusters while the colored ellipses correspond to 95\% confidence ellipses of the four groups from \citet{Spinks2005} and \citet{Spinks2010}.}
  \label{fig:gap_map}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width = \textwidth]{figure/gen_map}
  \caption{Comparison between reference classification of testing data set (upper left) and the estimated classifications based on the selected LDA-based classification (lda, upper right), multinomial logistic regression (multi, lower left) and random forest models (rf, lower right). Classification corresponds to the four classes as suggested by the hypothesis of \citet{Spinks2005} and \citet{Spinks2010}. 95\% confidence ellipses for the four classes are depicted and calculated from the initial assignments from the total dataset.}
  \label{fig:gen_map}
\end{figure}

% mean shapes of all the classes
\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.4\textwidth}
    \centering
    \includegraphics[width = \textwidth, height = 0.35\textheight, keepaspectratio = true]{figure/mshape_1}
    \caption{Northern}
    \label{fig:mean_shape1}
  \end{subfigure}
  \begin{subfigure}[b]{0.4\textwidth}
    \centering
    \includegraphics[width = \textwidth, height = 0.35\textheight, keepaspectratio = true]{figure/mshape_2}
    \caption{Eastern}
    \label{fig:mean_shape2}
  \end{subfigure}
  % new line. might want to make these closer together

  \begin{subfigure}[b]{0.4\textwidth}
    \centering
    \includegraphics[width = \textwidth, height = 0.35\textheight, keepaspectratio = true]{figure/mshape_3}
    \caption{Western}
    \label{fig:mean_shape3}
  \end{subfigure}
  \begin{subfigure}[b]{0.4\textwidth}
    \centering
    \includegraphics[width = \textwidth, height = 0.35\textheight, keepaspectratio = true]{figure/mshape_4}
    \caption{Southern}
    \label{fig:mean_shape4}
  \end{subfigure}
  \caption{Thin-plate splines for each of the four classes from the best classification hypothesis based on the generalization results (Fig. \ref{fig:gen_res}). The four different classes are labeled according to the biogeographic groups as depicted in figure \ref{fig:gen_map}. The deformations are depicted with 2x magnification from base.}
  \label{fig:mean_shape}
\end{figure}
